New_Data_Coherence

### 2019-08-20 Analysis/Coherence_Calculations_New.Rmd
update coherence

#Read in KEGG pathways for coherence
msig = readRDS("KEGG_String.rds")
#msig =msig %>% filter(Category == "KEGG")
coherence_tab = bind_rows()
for (i in unique(dis_slopes_string_count$Disease)) {
  #Filter to only include specific disease coherence
  dis = dis_slopes_string_count %>% filter(Disease == i)

@@

```{r}
msig = readRDS("KEGG_String_Filt.rds")
#msig =msig %>% filter(Category == "KEGG")
coherence_tab = bind_rows()
for (i in unique(dis_slopes_string_filt_count$Disease)) {
  print(i)
  dis = dis_slopes_string_filt_count %>% filter(Disease == i)
  msigs = msig %>% mutate(Num_Genes = abs(Count-dis$Count)) %>% arrange(Num_Genes)
  msigs = msigs[msigs$Num_Genes %in% unique(msigs$Num_Genes)[1:10],]

@@

```{r}
msig = readRDS("KEGG_Biogrid.rds")
#msig =msig %>% filter(Category == "KEGG")
coherence_tab = bind_rows()
for (i in unique(dis_slopes_biogrid_count$Disease)) {
  print(i)
  dis = dis_slopes_biogrid_count %>% filter(Disease == i)
  msigs = msig %>% mutate(Num_Genes = abs(Count-dis$Count)) %>% arrange(Num_Genes)
  msigs = msigs[msigs$Num_Genes %in% unique(msigs$Num_Genes)[1:10],]

@@

```{r}
msig = readRDS("Msigdf.rds")
msig =msig %>% filter(Category == "REACTOME") %>% filter(!is.na(Slope))
coherence_tab = bind_rows()
for (i in unique(dis_slopes_string_count$Disease)) {
  print(i)
  dis = dis_slopes_string_count %>% filter(Disease == i)
  msigs = msig %>% mutate(Num_Genes = abs(Count-dis$Count)) %>% arrange(Num_Genes)
  msigs = msigs[msigs$Num_Genes %in% unique(msigs$Num_Genes)[1:10],]

@@

```{r}
msig = readRDS("Msigdf.rds")
msig =msig %>% filter(Category == "REACTOME") %>% filter(!is.na(Slope))
coherence_tab = bind_rows()
for (i in unique(dis_slopes_string_filt_count$Disease)) {
  print(i)
  dis = dis_slopes_string_filt_count %>% filter(Disease == i)
  msigs = msig %>% mutate(Num_Genes = abs(Count-dis$Count)) %>% arrange(Num_Genes)
  msigs = msigs[msigs$Num_Genes %in% unique(msigs$Num_Genes)[1:10],]

@@

```{r}
msig = readRDS("Msigdf.rds")
msig =msig %>% filter(Category == "REACTOME") %>% filter(!is.na(Slope))
coherence_tab = bind_rows()
for (i in unique(dis_slopes_biogrid_count$Disease)) {
  print(i)
  dis = dis_slopes_biogrid_count %>% filter(Disease == i)
  msigs = msig %>% mutate(Num_Genes = abs(Count-dis$Count)) %>% arrange(Num_Genes)
  msigs = msigs[msigs$Num_Genes %in% unique(msigs$Num_Genes)[1:10],]

@@

```{r}
msig = readRDS("Msigdf.rds")
msig =msig %>% filter(Category == "CC") %>% filter(!is.na(Slope))
coherence_tab = bind_rows()
for (i in unique(dis_slopes_string_count$Disease)) {
  print(i)
  dis = dis_slopes_string_count %>% filter(Disease == i)
  msigs = msig %>% mutate(Num_Genes = abs(Count-dis$Count)) %>% arrange(Num_Genes)
  msigs = msigs[msigs$Num_Genes %in% unique(msigs$Num_Genes)[1:10],]

@@

```{r}
msig = readRDS("Msigdf.rds")
msig =msig %>% filter(Category == "CC") %>% filter(!is.na(Slope))
coherence_tab = bind_rows()
for (i in unique(dis_slopes_string_filt_count$Disease)) {
  print(i)
  dis = dis_slopes_string_filt_count %>% filter(Disease == i)
  msigs = msig %>% mutate(Num_Genes = abs(Count-dis$Count)) %>% arrange(Num_Genes)
  msigs = msigs[msigs$Num_Genes %in% unique(msigs$Num_Genes)[1:10],]

@@

```{r}
msig = readRDS("Msigdf.rds")
msig =msig %>% filter(Category == "CC") %>% filter(!is.na(Slope))
coherence_tab = bind_rows()
for (i in unique(dis_slopes_biogrid_count$Disease)) {
  print(i)
  dis = dis_slopes_biogrid_count %>% filter(Disease == i)
  msigs = msig %>% mutate(Num_Genes = abs(Count-dis$Count)) %>% arrange(Num_Genes)
  msigs = msigs[msigs$Num_Genes %in% unique(msigs$Num_Genes)[1:10],]

@@

```{r}
#Random networks

kegg_string = readRDS("msigdf.rds") %>% filter(Category == "KEGG")

kegg_string_filt = readRDS("KEGG_String_Filt.rds")

kegg_biogrid = readRDS("KEGG_String.rds")

ke

#String

string_random = bind_rows()
for (i in kegg_string$Count) {   
  j = 0
  diseases = bind_rows()
    while(j<11) {
    diseases_curr = GeneSample(i, string, directed = FALSE)
    diseases_curr = data.frame(Gene = names(diseases_curr$internal_connectivity), Internal = sqrt(diseases_curr$internal_connectivity), External = sqrt(diseases_curr$external_connectivity))
    if (any(diseases_curr$Internal !=0)) {
      j = j+1
      diseases = bind_rows(diseases, diseases_curr)

      mod_rand = lm(External ~ Internal-1, data = diseases)
      diseases_curr = data.frame(Count = i, Slope = coef(mod_rand)[1])
      string_random = bind_rows(string_random, diseases_curr)
      print(string_random)
}

saveRDS(string_random, "string_random_edges.rds")

#String Filtered

string_random_filt = bind_rows()
for (i in unique(kegg_string_filt$Count)) {   
  j = 0
    while(j<11) {
    diseases_curr = GeneSample(i, string_filt, directed = FALSE)
    diseases_curr = data.frame(Gene = names(diseases_curr$internal_connectivity), Internal = sqrt(diseases_curr$internal_connectivity), External = sqrt(diseases_curr$external_connectivity))
    if (any(diseases_curr$Internal !=0)) {
      j = j+1
      mod = lm(sqrt(External) ~ sqrt(Internal)-1, data = diseases_curr)
      diseases_curr = data.frame(Count = i, Slope = coef(mod)[1])
      string_random_filt = bind_rows(string_random_filt, diseases_curr)
      print(string_random_filt)

    }
    }
}

#String Filtered

biogrid_random = bind_rows()
for (i in unique(kegg_biogrid$Count)) {   
  j = 0
    while(j<11) {
    diseases_curr = GeneSample(dis$Count, links, directed = FALSE)
    diseases_curr = data.frame(Gene = names(diseases_curr$internal_connectivity), Internal = sqrt(diseases_curr$internal_connectivity), External = sqrt(diseases_curr$external_connectivity))
    if (any(diseases_curr$Internal !=0)) {
      j = j+1
      mod = lm(sqrt(External) ~ sqrt(Internal)-1, data = diseases_curr)
      diseases_curr = data.frame(Count = i, Slope = coef(mod)[1])
      string_random = bind_rows(string_random, diseases_curr)
      print(string_random)

    }
    }
}

```{r}
string_random = string_random %>% group_by(Count) %>% summarise(Slope = median(Slope))
cor(string_random)

string_filt_random = string_filt_random %>% group_by(Count) %>% summarise(Slope = median(Slope))
cor(string_filt_random)
```

```{r}
msig_sum = readRDS("Msigdf.rds") %>% distinct() %>% filter(!grepl("_1", Category))

@@

```{r}
#Testing coherence and modularity relationship

#Binding disease select (Disease name) with modularity calculations

mod_string = readRDS("Modularity_String.rds")
mod_string_filt = readRDS("Modularity_String_Filt.rds")
mod_biogrid = readRDS("Modularity_Biogrid.rds")

mod_sum =data.frame(Disease = disease_select$Disease, Modularity_String = unlist(mod_string), Modularity_String_Filt = unlist(mod_string_filt), Modularity_Biogrid = unlist(mod_biogrid))

Mod_Frame = left_join(mod_sum, coherence_disease, "Disease")
Mod_Frame = Mod_Frame %>% dplyr::select(Disease, Category:`String Filt P-value`, `Modularity Biogrid` = Modularity_Biogrid, `Modularity String` = Modularity_String, `Modularity String Filt`= Modularity_String_Filt)
```

```{r}
mod_sum = ggplot(Mod_Frame, aes(x = `String Coherence KEGG`, y = `Modularity_String`)) + geom_point() + labs(x = "String Coherence KEGG", y = "Modularity String")

ggsave("./figures/Modularity_Coherence.png", mod_sum, height=5, width=7, units="in", dpi = 300)

write_xlsx(Mod_Frame, "./tables/Mod_Table.xlsx")

>>>>

#Read in KEGG pathways for coherence
msig = readRDS("KEGG_String.rds")
msig =msig %>% filter(Category == "CP:KEGG")
coherence_tab = bind_rows()
for (i in unique(dis_slopes_string_count$Disease)) {
  #Filter to only include specific disease coherence
  dis = dis_slopes_string_count %>% filter(Disease == i)

@@

```{r}
msig = readRDS("KEGG_String_Filt.rds")
msig =msig %>% filter(Category == "CP:KEGG")
coherence_tab = bind_rows()
for (i in unique(dis_slopes_string_filt_count$Disease)) {
  print(i)
  dis = dis_slopes_string_filt_count %>% filter(Disease == i)
  msigs = msig %>% mutate(Num_Genes = abs(Count-dis$Count)) %>% arrange(Num_Genes)
  msigs = msigs[msigs$Num_Genes %in% unique(msigs$Num_Genes)[1:10],]

@@

```{r}
msig = readRDS("KEGG_Biogrid.rds")
msig =msig %>% filter(Category == "CP:KEGG")
coherence_tab = bind_rows()
for (i in unique(dis_slopes_biogrid_count$Disease)) {
  print(i)
  dis = dis_slopes_biogrid_count %>% filter(Disease == i)
  msigs = msig %>% mutate(Num_Genes = abs(Count-dis$Count)) %>% arrange(Num_Genes)
  msigs = msigs[msigs$Num_Genes %in% unique(msigs$Num_Genes)[1:10],]

@@

```{r}
msig = readRDS("KEGG_String.rds")
msig =msig %>% filter(Category == "CP:REACTOME") %>% filter(!is.na(Slope))
coherence_tab = bind_rows()
for (i in unique(dis_slopes_string_count$Disease)) {
  print(i)
  dis = dis_slopes_string_count %>% filter(Disease == i)
  msigs = msig %>% mutate(Num_Genes = abs(Count-dis$Count)) %>% arrange(Num_Genes)
  msigs = msigs[msigs$Num_Genes %in% unique(msigs$Num_Genes)[1:10],]

@@

```{r}
msig = readRDS("KEGG_String_Filt.rds")
msig =msig %>% filter(Category == "CP:REACTOME") %>% filter(!is.na(Slope))
coherence_tab = bind_rows()
for (i in unique(dis_slopes_string_filt_count$Disease)) {
  print(i)
  dis = dis_slopes_string_filt_count %>% filter(Disease == i)
  msigs = msig %>% mutate(Num_Genes = abs(Count-dis$Count)) %>% arrange(Num_Genes)
  msigs = msigs[msigs$Num_Genes %in% unique(msigs$Num_Genes)[1:10],]

@@

```{r}
msig = readRDS("KEGG_Biogrid.rds")
msig =msig %>% filter(Category == "CP:REACTOME") %>% filter(!is.na(Slope))
coherence_tab = bind_rows()
for (i in unique(dis_slopes_biogrid_count$Disease)) {
  print(i)
  dis = dis_slopes_biogrid_count %>% filter(Disease == i)
  msigs = msig %>% mutate(Num_Genes = abs(Count-dis$Count)) %>% arrange(Num_Genes)
  msigs = msigs[msigs$Num_Genes %in% unique(msigs$Num_Genes)[1:10],]

@@

```{r}
msig = readRDS("KEGG_String.rds")
msig =msig %>% filter(Category == "CC") %>% filter(!is.na(Slope))
coherence_tab = bind_rows()
for (i in unique(dis_slopes_string_count$Disease)) {
  print(i)
  dis = dis_slopes_string_count %>% filter(Disease == i)
  msigs = msig %>% mutate(Num_Genes = abs(Count-dis$Count)) %>% arrange(Num_Genes)
  msigs = msigs[msigs$Num_Genes %in% unique(msigs$Num_Genes)[1:10],]

@@

```{r}
msig = readRDS("KEGG_String_Filt.rds")
msig =msig %>% filter(Category == "CC") %>% filter(!is.na(Slope))
coherence_tab = bind_rows()
for (i in unique(dis_slopes_string_filt_count$Disease)) {
  print(i)
  dis = dis_slopes_string_filt_count %>% filter(Disease == i)
  msigs = msig %>% mutate(Num_Genes = abs(Count-dis$Count)) %>% arrange(Num_Genes)
  msigs = msigs[msigs$Num_Genes %in% unique(msigs$Num_Genes)[1:10],]

@@

```{r}
msig = readRDS("KEGG_Biogrid.rds")
msig =msig %>% filter(Category == "CC") %>% filter(!is.na(Slope))
coherence_tab = bind_rows()
for (i in unique(dis_slopes_biogrid_count$Disease)) {
  print(i)
  dis = dis_slopes_biogrid_count %>% filter(Disease == i)
  msigs = msig %>% mutate(Num_Genes = abs(Count-dis$Count)) %>% arrange(Num_Genes)
  msigs = msigs[msigs$Num_Genes %in% unique(msigs$Num_Genes)[1:10],]

@@

```{r}
msig_sum = readRDS("KEGG_String.rds") %>% distinct() %>% filter(!grepl("_1", Category))

@@
